---
title: "NESREA Weekly Social Media Report"
author: "Prepared by Web Monitoring Group"
output: html_document
---

<!--
******************************************************************************
*                         GENERAL NOTICE                                     *
* This is a generic reporting format for the NESREA Web Monitoring Group.    *
* To easily use it click on 'Knit' in the toolbar above (applies to RStudio).*
******************************************************************************
                                                                           -->
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE, message = FALSE, include = FALSE}
packrat::off()

pkglist <- c("dplyr",
             "ggplot2",
             "lubridate",
             "qdap",
             "stringr",
             "tm",
             "twitteR",
             "wordcloud")
not_installed <- pkglist[!pkglist %in% installed.packages()[, "Package"]]
if (length(not_installed))
  install.packages(not_installed)
lapply(pkglist, library, character.only = TRUE)


source_but_also_check_for <- function(ff) {
  if (file.exists(ff)) {
    source(ff)
  } else {
      warning(paste(sQuote(ff), "was not found in the working directory"))
    }
}

source_but_also_check_for("twitter-functions.R")

rm(source_but_also_check_for, pkglist, not_installed)
```

#### Executive Summary 
Date of Report: `r format(today(), "%A, %d %B %Y")`  

```{r, echo=FALSE, message=FALSE}

                      ##############
                      #  TWITTER   #
                      ##############
# Access stored tweets
register_sqlite_backend("data/nesreanigeria.db") 
all_data <- load_tweets_db(as.data.frame = TRUE, "nesreanigeria_tweets")

# Check the date of the newest stored tweet
# if less than today()
if (as.Date(all_data$created[nrow(all_data)]) < today())
  warning("The database may be outdated.\nRun 'logon_to_twitter() followed by 'update_nesrea_db()' to update it before knitting the document.")

# Processing...
all_data$date_only <- as.Date(all_data$created)
wk_data <- filter(all_data, date_only >= (today()-7) & date_only <= (today()-1))
last_wk <- filter(all_data, date_only >= (today()-14) & date_only <= (today()-8))
wk_data$text <- str_replace_all(wk_data$text, "[^[:graph:]]", " ")

# Statistics
no.wk <- nrow(wk_data)
month_begin <- floor_date(today(), "month")
month_end <- ceiling_date(today(), "month")
mth_data <- filter(all_data, date_only >= month_begin & date_only <= month_end)
mostRTed <- wk_data$text[which.max(wk_data$retweetCount)]
mostFaved <- wk_data$text[which.max(wk_data$favoriteCount)]
```

|Twitter                                  |                   |
|-----------------------------------------|-------------------|
|No. of tweets in `r format(today(), "%B")` | `r nrow(mth_data)`|
|No of tweets in past 7 days              | `r no.wk`         |
|Most Retweeted                           | `r mostRTed`      |
|Most Liked                               | `r mostFaved`     |  

```{r, echo=FALSE, message=FALSE}
#                         ############
#                         # Facebook #
#                         ############
# # Direct authentication applied
# source("fb_authentication.R")
# 
# # Selects type of insight to be loaded (wrapper for Rfacebook::getinsights())
# chooseInsight <- function(type = c("page_fan_adds", "page_fan_removes",
#                               "page_views_login", "page_views_logout",
#                               "page_views", "page_story_adds",
#                               "page_impressions", "page_posts_imporessions",
#                               "page_consumptions", "post_consumptions_by_type",
#                               "page_fans_country")) {
#   result <- getInsights(object_id = NESREA_page_id,
#                         token = NESREA_token,
#                         metric = type,
#                         version = API_version)
#   result <- select(result, value:end_time)
#   result$end_time <- substr(result$end_time,
#                             start = 1,
#                             stop = regexpr("T", result$end_time) - 1)
#   result 
# }
# 
# # Apply the function
# newFans <- chooseInsight("page_fan_adds")
# fansLeft <- chooseInsight("page_fan_removes")
# newStories <- chooseInsight("page_story_adds")
# pageImpressions <- chooseInsight("page_impressions")
# postImpressions <- chooseInsight("page_posts_impressions")
# pageConsumptions <- chooseInsight("page_consumptions")
# 
# # PUblic posts
# # Load data on Page posts
# page_posts <- getPage(page = "nesreanigeria",
#                       since = format(today()-7, "%Y/%m/%d"),
#                       until = format(today(), "%Y/%m/%d"),
#                       reactions = TRUE,
#                       token = NESREA_token,
#                       feed = TRUE,
#                       verbose = FALSE)
# if (dim(page_posts)[1] == 0) {
#   page_posts <- NULL
#   mth_Posts <- NULL
#   wk_Posts <- NULL
#   noPosts <- "No posts in the last week"
# } else {
#   page_posts <- select(c(message:type, likes_count:shares_count))
# 
#   colnames(page_posts) <- gsub("_count$|_time$", "", colnames(page_posts))
#   
#   page_posts$message <- page_posts$message %>%
#     gsub("[^[:graph:]]", "", .) %>%
#     str_trim(.)
#   
#   page_posts$type <- as.factor(page_posts$type)
#   
#   page_posts$created <- substr(page_posts$created,
#                                start = 1,
#                                stop = regexpr("T", page_posts$created) - 1)
#   
#   mth_Posts <- filter(page_posts,
#                       created >= month_begin && created <= month_end)
#   
#   wk_Posts <- filter(page_posts,
#                      created >= today()-7 && created <= today())
#   
# }
# 
# # Miscellaneous string object
# ourFbPosts <- "No. of Page posts by us in"

```
<!--
|Facebook                                  |                            |
|------------------------------------------|----------------------------|
|`r # paste(ourFbPosts, format(today(), "%B"))`|`r # nrow(mth_Posts)`         |
|`r #paste(ourFbPosts, "past 7 days")`      |`r # nrow(wk_Posts)`          |
|Most Liked Post  (Overall)                |`r # max(page_posts$liked)`   |
|Most Liked Post (`r # format(today(), "%B")`) |`r # no code yet`           |
|Most Shared Post                          |`r # max(page_posts$shares)`  |
|Most Commented                            |`r # max(page_posts$comments)`|
|                        |`r # if (is.null(page_posts)) paste (noPosts)`  |
-->
***
### 1.0 Introduction  
<!-- TEXT SHOULD GO BELOW THIS LINE -->
This is the Social Media Monitoring Report for the week beginning `r format(today() - 7, "%A, %d %B %Y")`. The report is based on data obtained from the following NESREA-owned platforms:

1. Twitter
2. Facebook
3. NESREA website  
<!-- DO NOT WRITE BELOW THIS LINE-->  

#### 1.1 Twitter Analysis
```{r, echo=FALSE, message=FALSE}
tweets_by_us <- filter(wk_data, screenName == "NESREANigeria")

busiest_day <- which.max(table(wk_data$date_only))
busiest_day <- ymd(names(busiest_day))
```

##### 1.1.1 Summary statistics for the week
<!-- INSERT ADDITIONAL TEXT BELOW THIS LINE -->
|       Description                     |    Result                        |
|---------------------------------------|----------------------------------|
|Total number of tweets **by** NESREA:  | `r nrow(tweets_by_us)`           |
|Total number of tweets **on** NESREA   | `r nrow(wk_data)`                |
|Average number of tweets per day:      | `r floor(nrow(wk_data)/7)`       |
|Day of highest activity:               | `r format(busiest_day, "%d %B")` |
|Top 5 influential handles:             | `r print("---")`                 |
|Most liked tweet:                      | `r mostFaved`                    |
|Most retweeted tweet:                  | `r mostRTed`                     |
|Comparative tweet volume (week-on-week)| `r ifelse((no.wk > 0), paste0("+", no.wk), no.wk)  `|
|                                       |                                  |  

<!-- DO NOT ENTER TEXT BELOW THIS LINE -->
##### 1.1.2 Distribution of tweets mentioning NESREA  
The tweets are plotted as a smoothed density plot - the pink graph represents original tweets, while the blue one is for retweets.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
distr <- ggplot(wk_data, aes(created)) +
  geom_density(aes(fill = isRetweet), alpha = .5) +
  theme(legend.justification = c(1, 1), legend.position = c(1, 1)) +
  xlab("Date") +
  ggtitle(paste("Distribution of tweets for", format(min(wk_data$created), "%d %b"), "to", format(max(wk_data$created), "%d %b %Y")))

distr
```

<!--- For specific days of the week; to be used only if there is anything of interest. Note that if there are insufficent data, the plot will not be drawn. To use this code chunk change the argument below to 'eval = TRUE' -->

<!-- INSERT ADDITIONAL TEXT BELOW THIS LINE -->

<!-- DO NOT ENTER TEXT BELOW THIS LINE -->
```{r, echo=FALSE, eval=FALSE}  
dayOf <- filter(wk_data, mday(created) == 7)
distr_day <- ggplot(dayOf, aes(created)) +
  geom_density(aes(fill = isRetweet), alpha = .5) +
  theme(legend.justification = c(1, 1), legend.position = c(1, 1)) +
  xlab("Time") +
  ggtitle("Tweets on... ")

distr_day
```

##### 1.1.3 Sentiment Analysis  
<!-- INSERT ADDITIONAL TEXT BELOW THIS LINE -->
A Sentiment Analysis was carried out and the data displayed in the form of a dot chart and a word cloud.

###### **1.1.3.1 Dot chart of sentiments**
The dot charts plot positive and negative words, respectively. 
<!-- INSERT ADDITIONAL TEXT BELOW THIS LINE -->

```{r, echo=FALSE, message=FALSE, warning=FALSE}
spl <- split(wk_data, wk_data$isRetweet)
orig <- spl[['FALSE']]
RT <- mutate(spl[['TRUE']], sender = substr(text, 5, regexpr(':', text) - 1))

pol <- lapply(orig$text, function(txt) {
  gsub("(\\.|!|\\?)+\\s+|(\\++)", " ", txt) %>% 
    gsub(" http[^[:blank:]]+", "", .) %>% 
    polarity(.)
})
orig$emotionalValence <- sapply(pol, function(x) x$all$polarity)

polWordTable <- sapply(pol, function(p) {
  words <- c(positiveWords = paste(p$all$pos.words[[1]], collapse = ' '),
            negativeWords = paste(p$all$neg.words[[1]], collapse = ' '))
  gsub('-', '', words) 
}) %>%
  apply(1, paste, collapse = ' ') %>%
  stripWhitespace() %>%
  strsplit(' ') %>%
  sapply(table, simplify = FALSE)

oldpar <- par()
par(mfrow = c(1, 2))
invisible(
  lapply(1:2, function(i) {
    dotchart(sort(polWordTable[[i]]), cex = .8)
    mtext(names(polWordTable)[i])
  }))

par(oldpar) 
```
<!-- INSERT ADDITIONAL TEXT BELOW THIS LINE -->

* **Most positive tweet:** `r orig$text[which.max(orig$emotionalValence)]`
* **Most negative tweet:** `r orig$text[which.min(orig$emotionalValence)]`  
<!-- INSERT ADDITIONAL TEXT BELOW THIS LINE -->

###### **1.1.3.2 Word cloud of sentiments**
The word cloud below represents common words that were clustered around negative, neutral or positive terms; the size of each word represents the relative frequency of its occurence. Thus words with the largest font size occured more frequently than those with smaller fonts.
```{r, echo=FALSE, warning=FALSE, message=FALSE}
make_corpus <- function(GText, stem = TRUE) {
  corp <- VCorpus(VectorSource(GText)) %>% 
    tm_map(removePunctuation) %>%
    tm_map(stripWhitespace) %>%
    tm_map(content_transformer(tolower)) %>%
    tm_map(removeWords, stopwords("english"))
  if(stem)
    corp <- tm_map(corp, stemDocument) 
  
  names(corp) <- names(GText)
  corp
}

color <- function() {
  require(RColorBrewer)
  col <- brewer.pal(3, 'Paired')
  col
}

polSplit <- split(orig, sign(orig$emotionalValence))

if (nrow(polSplit[[1]]) == 0 | 
    nrow(polSplit[[2]]) == 0 |
    nrow(polSplit[[3]]) == 0)
  warning("Insufficient data to render the wordcloud\n")

polText <- sapply(polSplit, function(df) {
  paste(tolower(df$text), collapse = ' ') %>%
    gsub(' http|@)[^[:blank:]]+', '', .) %>%  
    gsub('[[:punct:]]', '', .)  
}) %>%
  structure(names = c('negative', 'neutral', 'positive'))

  polText['negative'] <- removeWords(polText['negative'],
                                 names(polWordTable$negativeWords))
  polText['positive'] <- removeWords(polText['positive'],
                                     names(polWordTable$positiveWords))
  
  corp <- make_corpus(polText)
  col3 <- RColorBrewer::brewer.pal(3, 'Paired') 
  comparison.cloud(as.matrix(TermDocumentMatrix(corp)),
                   max.words = 150, min.freq = 1, 
                   random.order = FALSE, rot.per = 0,
                   colors = col3, vfont = c("sans serif", "plain"))
```

<!-- INSERT ADDITIONAL TEXT BELOW THIS LINE -->


<!---
### Facebook Analysis
### Total number of posts

# Website Analysis
In progress...
-->
### 2.0 Observations  
<!-- INSERT ADDITIONAL TEXT BELOW THIS LINE -->

### 3.0 Recommendation  
<!-- INSERT ADDITIONAL TEXT BELOW THIS LINE -->

```{r, echo=FALSE}
victor <- person("Victor", "Ordu", email =  "victor.ordu@nesrea.gov.ng", comment = "Chairman Web Monitoring Group")
remi <- person("Remi", "Agunbiade", email = "remi.agunbiade@nesrea.gov.ng", comment = "Member, Web Monitoring Group")
amaka <- person("Amaka", "Ejiofor", email = "amaka.ejiofor@nesrea.gov.ng", comment = "Member, Web Monitoring Group")
eze <- person("Ezechinyere", "Achilefu", email = "ezechinyere.achilefu@nesrea.gov.ng", comment = "Member, Web Monitoring Group")
```

Submitted by:

`r paste(victor$given, victor$family)`  
`r victor$comment`