---
title: "NESREA Weekly Social Media Report"
author: "Web Monitoring Group"
date:
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

today <- Sys.time()
```

**Summary**

**Date of Report**: `r format(today, "%A, %d %B %Y")`

Twitter
```{r, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
library(ggplot2)
library(lubridate)

twitteR::register_sqlite_backend("shinyNESREA/data/nesreanigeria.db")
all_data <- twitteR::load_tweets_db(as.data.frame = TRUE, "nesreanigeria_tweets")

all_data$date_only <- as.Date(all_data$created)
wk_data <- dplyr::filter(all_data, date_only >= "2017-02-07" & date_only <= "2017-02-14")
wk_data$text <- stringr::str_replace_all(wk_data$text, "[^[:graph:]]", " ")

```

|Detail                    |Result             |
|--------------------------|-------------------|
|Total number of tweets    | `r nrow(all_data)`|
|No of tweets for the week | `r nrow(wk_data)` |
|Most positive tweet       | *(put data here)* |
|Most negative tweet       | *(put data here)* |

Facebook

| Detail                    |Result             |
|---------------------------|-------------------|
|Total number of Page posts | *(put data here)* |
|Total number of new Likes  | *(put data here)* |
|Overall number of Likes    | *(put data here)* |
|Total number of Comments   | *(put data here)* |

***

### Twitter Analysis
#### Summary statistics for the week
#### Distribution of tweets mentioning NESREA
```{r, echo=FALSE}
distr <- ggplot(wk_data, aes(created)) +
  geom_density(aes(fill = isRetweet), alpha = .5) +
  theme(legend.justification = c(1, 1), legend.position = c(1, 1)) +
  xlab("Tweets")

distr
```

<!--- ### On specific days -->
```{r, echo=FALSE, eval=FALSE}  
dayOf <- dplyr::filter(wk_data, mday(created) == 7)
distr_day <- ggplot(dayOf, aes(created)) +
  geom_density(aes(fill = isRetweet), alpha = .5) +
  theme(legend.justification = c(1, 1), legend.position = c(1, 1)) +
  xlab("Tweets on... ")
```

### Emotions
#### Dot chart of sentiment
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tm)
library(qdap)
library(stringr)
spl <- split(wk_data, wk_data$isRetweet)
orig <- spl[['FALSE']]
RT <- dplyr::mutate(spl[['TRUE']], sender = substr(text, 5, regexpr(':', text) - 1))
pol <- lapply(orig$text, function(txt) {
  gsub("(\\.|!|\\?)+\\s+|(\\++)", " ", txt) %>% 
    gsub(" http[^[:blank:]]+", "", .) %>% 
    polarity(.)
})
orig$emotionalValence <- sapply(pol, function(x) x$all$polarity)
polWordTable <- sapply(pol, function(p) {
  words = c(positiveWords = paste(p[[1]]$pos.words[[1]], collapse = ' '),
            negativeWords = paste(p[[1]]$neg.words[[1]], collapse = ' '))
  gsub('-', '', words) 
}) %>%
  apply(1, paste, collapse = ' ') %>%
  stripWhitespace() %>%
  strsplit(' ') %>%
  sapply(table)

oldpar <- par()
par(mfrow = c(1, 2))
invisible(
  lapply(1:2, function(i) {
    dotchart(sort(polWordTable[[i]]), cex = .8)
    mtext(names(polWordTable)[i])
  }))

par(oldpar) 
```

**Most positive tweet:** `r orig$text[which.max(orig$emotionalValence)]`

**Most negative tweet:** `r orig$text[which.min(orig$emotionalValence)]`

#### Word cloud
```{r, echo=FALSE, warning=FALSE}
library(wordcloud)
make_corpus <- function(GText, stem = TRUE) {
  corp <- VCorpus(VectorSource(GText)) %>% 
    tm_map(removePunctuation) %>%
    tm_map(stripWhitespace) %>%
    tm_map(content_transformer(tolower)) %>%
    tm_map(removeWords, stopwords("english"))
  if(stem)
    corp <- tm_map(corp, stemDocument) 
  
  names(corp) <- names(GText)
  corp
}

color <- function() {
  require(RColorBrewer)
  col <- brewer.pal(3, 'Paired')
  col
}

polSplit <- split(orig, sign(orig$emotionalValence))
polText <- sapply(polSplit, function(df) {
  paste(tolower(df$text), collapse = ' ') %>%
    gsub(' http|@)[^[:blank:]]+', '', .) %>%  
    gsub('[[:punct:]]', '', .)  
}) %>%
  structure(names = c('negative', 'neutral', 'positive'))

polText['negative'] <- removeWords(polText['negative'],
                                   names(polWordTable$negativeWords))
polText['positive'] <- removeWords(polText['positive'],
                                   names(polWordTable$positiveWords))

corp <- make_corpus(polText)
col3 <- RColorBrewer::brewer.pal(3, 'Paired') 
comparison.cloud(as.matrix(TermDocumentMatrix(corp)),
                 max.words = 150, min.freq = 1, 
                 random.order = FALSE, rot.per = 0,
                 colors = col3, vfont = c("sans serif", "plain"))
```

<!---
# Facebook Analysis
In progress...

# Website Analysis
In progress...

# Observations

# Conclusions
-->
### About the report
This report of social media activity on platforms owned by NESREA, namely [Twitter](http::/twitter.com/nesreanigeria) and [Facebook](http://facebook.com/NESREANigeria), and focuses primarily on citizens' engagement with the Agency's via these platforms.

The data are downloaded via access to the application programming interface (API)  of the respective sites and analysed with the R programming language.[^1] This document was generated with R Markdown to allow programmmatic rendering of outputs.[^2] The complete code behind this presentation can be found  **[here](https://raw.githubusercontent.com/NESREA/NESREA_social/master/weekly-report-generic.Rmd)**.


[^1]: The R Programming Language for Statistical Computing was used for all the analyses.
[^2]: The document is generated with R Markdown.