---
title: "Facebook"
author: "Web Monitoring Group"
date: 
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
# Preliminaries
Load and attach packages, as well as custom functions
```{r dependencies, echo=TRUE, results='hide'}
suppressPackageStartupMessages(
  invisible(
    lapply(c("DBI", "RSQLite", "Rfacebook", "dplyr", "ggplot2", "tidyr"),
           library,
           character.only = TRUE)
  )
)

source("fb-functions.R")
```

# Data collection
Fetch the Page's Newsfeed from the local database. A summary of the available data is displayed.
```{r retrieve-data}
if (!exists("con")) {
  con <- dbConnect(SQLite(), "../data/nesreanigeria.db")
  
  posts <- dbReadTable(con, "nesreanigeria_fbposts")
  likes <- dbReadTable(con, "nesreanigeria_fblikes")
  comments <- dbReadTable(con, "nesreanigeria_fbcomments")
  
  dbDisconnect(con)
  suppressWarnings(rm(con))
}

dfs <- list(posts = posts,
            likes = likes,
            comments = comments)
glimpse(dfs$posts)
```

```{r}
glimpse(dfs$likes)
```

```{r}
glimpse(dfs$comments)
```


Note that the function `getPage()` is used to collect these posts through the Facebook API/Rfacebook package. It can equally be used to harvest data from others' public posts via the `page` argument.


# Data cleaning  
We have a user-defined function we have called `prepare_data()` that lives in the file *fb-functions* that was sourced earlier and it will help us do some data cleaning very quickly.  

The function:

- takes a data frame as an argument
- checks that the column names match those of typical Facebook post data
- removes non-human readable characters from the 'message' variable
- changes 'type' from a character to a categorical variable
- converts 'time' into a Date-Time object (POSIX standard)
- returns the modified data frame  

This is what the function definition looks like:  
```{r prepare_data-definition, results='hold'}
prepare_data
```

Also columns 1 and 2 are redundant for the purpose of these particular analyses and will be removed. This is how it's done and the data now look like this  
```{r clean-data, echo=TRUE}
posts <- posts %>%
  prepare_data() %>%
  select(message:shares_count)

glimpse(posts)
```


```{r density dist: FB posts}
ggplot(posts, aes(created_time)) +
  geom_density(fill = "lightblue") +
  ggtitle("Distribution of Facebook posts")
```

```{r}
gg <- ggplot(posts, aes(created_time, likes_count)) +
  geom_point() +
  labs(title = "Scatterplot of Facebook Post Likes",
       y = "No. of Likes") 
  
gg

```


```{r}
ggplot(posts, aes(type)) + geom_bar(aes(fill = type)) +
  labs(title = "Bar chart of Types of Facebook Posts")
```

```{r}
## Remove outlier
adj.posts <- filter(posts, likes_count < 500)

ggplot(adj.posts, aes(type, likes_count)) +
  geom_boxplot(aes(fill = type)) +
  labs(title = "Total Likes vs Type of Post",
       caption = "NB: A photo post that attracted > 500 likes was omitted")
```

```{r}
gg_likes <- ggplot(posts, aes(likes_count))

gg_likes + 
  geom_histogram(aes(fill = type)) +
  facet_wrap( ~ type)
```


```{r}
adj.posts <- filter(posts, comments_count < max(comments_count))

ggplot(adj.posts, aes(type, comments_count)) +
  geom_boxplot(aes(fill = type)) +
  labs(title = "Total Comments vs. Type of Post")
```


```{r}
ggplot(posts, aes(comments_count)) + geom_histogram(fill = "blue")
```


```{r}
gg_comments <- ggplot(posts, aes(comments_count))

gg_comments +
  geom_histogram(aes(fill = type)) +
  facet_wrap( ~ type)
```



```{r}
gg_shares <- ggplot(posts, aes(shares_count))
gg_shares +
  geom_histogram(fill = "darkgreen") +
  labs(title = "Histogram of Post 'Shares'",
       x = "No. of times shared")
```

```{r}
gg_shares +
  geom_histogram(aes(fill =  type)) +
  facet_wrap( ~ type)
```

```{r}
ggplot(posts, aes(type, shares_count)) +
  geom_boxplot(aes(fill = type)) +
  labs(title = "Shares vs Type of Post",
       y = "No. of 'Shares'")
```


Like details

```{r}
top10Likers <- 
  head(sort(table(likes$from_name, dnn = c(NULL, "Name")), decreasing = TRUE), n = 10L) %>%
  as.data.frame(.)
  
top10Likers
```

```{r}
ggplot(top10Likers, aes(Name, Freq)) +
  geom_col(fill = "violet") +
  coord_flip()
```


```{r}
nesrea <- "National Environmental Standards & Regulations Enforcement Agency"

top10Commenters <- 
  table(comments$from_name, dnn = c(NULL, "Name")) %>%
  sort(decreasing = TRUE) %>%
  as.data.frame() %>%
  filter(Name != nesrea) %>%
  slice(1:10)

top10Commenters
```

```{r}
ggplot(top10Commenters, aes(Name, Freq)) +
  geom_col(fill = "blue") +
  coord_flip()
```
